\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4in,top=0.4in,right=0.4in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\usepackage{enumitem} % For compact lists
\renewcommand{\baselinestretch}{0.95} % Reduce line spacing
\usepackage{hyperref} % For clickable links
\hypersetup{
    colorlinks=true,
    urlcolor=blue
}
\name{Sangam Mundhe} % Your name
\address{+91 9370645756 \\ Pune, India} 
\address{\href{mailto:sangammunde3@gmail.com}{Email} \\ \href{https://linkedin.com/in/sangammundhe}{LinkedIn} \\ 
\href{https://linktr.ee/sangammundhe}{AllLink} \\
\href{https://sangammundhe5756.onrender.com}{Portfolio}}\\


\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{Objective}
Aspiring Software Engineer pursuing a Bachelor's in Computer Engineering with 1+ year of full-stack experience. Seeking a Software Engineering Internship  to apply skills.
\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
{\bf Bachelor of Engineering in Computer Engineering}, PDEA’s College of Engineering, Pune \hfill {Expected 2025}\\
CGPA: 9+ \href{https://drive.google.com/file/d/1EidP7nXszFpSvDOavsjf9RyhIsCIaI4V/view}{View}} | Relevant Coursework: Data Structures, Algorithms, Software Engineering, Machine Learning
\end{rSection}

%----------------------------------------------------------------------------------------
% SKILLS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{4ex}} l }
Languages & Proficient in JavaScript, Python, Java  \\
Frontend & HTML, CSS, JavaScript, React, Redux, Tailwind CSS, MUI, Bootstrap \\
Backend & Node.js, Express.js, REST APIs, JWT\\
Databases & MongoDB, SQL, PostgreSQL \\
Tools & Git, GitHub, Render, Unix/Linux \\
Soft Skills & Communication, Teamwork, Problem-solving
\end{tabular}
\end{rSection}

%----------------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\textbf{Full-Stack Developer Intern}, Capabl India \hfill May 2024 - Jun 2024 \\
Remote - Pune, India
\begin{itemize}[noitemsep, topsep=0pt, leftmargin=*]
    \item Developed a dynamic application using React, enhancing front-end UX and state management.
    \item Utilized React.js, HTML, CSS, JavaScript, and Tailwind CSS, contributing to front-end and MERN stack.
\end{itemize}

\textbf{Intern Weather Dashboard}\href{https://weather-app-d00u.onrender.com/}{ (Link)} \hfill Summer 2023 \\
Developed a weather dashboard using React and Tailwind CSS, focusing on UI/UX and data performance optimization.

\end{rSection}

%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects}

\item \textbf{Pet Adoption (PetFriend)} (\href{https://petfriend5756.onrender.com/}{Link}) \hfill Jul 2024 - Aug 2024 \\
Developed a pet adoption and management application using the MERN stack.

\item \textbf{E-commerce Website} (\href{https://estore-sangam5756.onrender.com}{Link}) \hfill Jun 2024 - Jul 2024 \\
Built using the MERN stack; integrated secure authentication and payment systems.

\item \textbf{GitHub Clone} (\href{https://github.com/Sangam5756/mern-github-app}{Link}) \hfill May 2024 - Jun 2024 \\
Built a GitHub clone using the MERN stack with features like authentication and repo search.

\item \textbf{Admin Employee Management System} (\href{https://github.com/Sangam5756/Employee_Management_Admin_Panel}{Link}) \hfill Apr 2024 - May 2024 \\
Created a responsive employee management system using Express, Node.js, and MySQL with CRUD operations and MVC architecture.

\item \textbf{Weather App} (\href{https://weather-app-d00u.onrender.com/}{Link}) \hfill Mar 2024 \\
Developed a React-based app providing real-time weather updates, including live location and forecasts.

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXTRA-CURRICULAR ACTIVITIES SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Extra-Curricular Activities} 
\begin{itemize}[noitemsep, topsep=0pt, leftmargin=*]
    \item Active GitHub contributor with personal and collaborative projects.
    \item Regularly participates in LeetCode contests; daily problem-solving to refine algorithms.
    \item Volunteered as a coding mentor, guiding beginners in programming fundamentals.
\end{itemize}
\end{rSection}

%----------------------------------------------------------------------------------------
%	CERTIFICATIONS AND ACHIEVEMENTS SECTION
%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
%	AVAILABILITY SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Availability}
Available for a full-time internship of at least 6 months, outside of university term time.
\end{rSection}

\end{document}